Environmental stress affects niche breadth in plant-pollinator communities

### 2019-11-16 paper/manuscript.Rmd
Explain why models with potential number of partners are stringent

We evaluate four models to assess the relative importance of suitability. 
A first model, our baseline model, included three population-level predictors and two grouping levels, species and the community. 
The population-level predictors in the baseline model, commonly called fixed effects, were the habitat suitability, the species guild (plant or a pollinator), and its number of known possible partners.
We included the number of known possible partners as a predictor in our models as it allows us to control for the environmental effects on species co-occurrence. 
We calculate this metric by determining the number of partners with which the species is known to interact in any other community.
Controlling for the number of potential partners makes our model a particularly stringent test of our environmental stress hypotheses. 
Often the potential and the actual number of partners is the same or very close to each other, especially for rare species present only in a few communities.  
As we were interested in understanding whether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we, therefore, included guild and its interaction with suitability in the model. 
We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate two questions. 
First, it allows us to inspect the extent to which suitability is a population or a group level effect. 
Second, by investigating the correlation between the intercept and the slope as a model parameter, it allowed us to inspect the extent by which species with a small or large number of interactions respond to increasing levels of environmental stress. 
To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we also calculated an intercept for each community in our study.
To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit standard deviation.

>>>>

We evaluate four models to assess the relative importance of suitability. 
A first model, our baseline model, included three population-level predictors and two grouping levels, species and the community. 
The population-level predictors in the baseline model, commonly called fixed effects, were the habitat suitability, the species guild (plant or a pollinator), and its number of known possible partners.
We included the number of known possible partners as a predictor in our models as it allows us to control for the environmental effects on species co-occurrence. 
We calculate this metric by determining the number of partners with which the species is known to interact in any other community.
Controlling for the number of potential partners makes our model a particularly stringent test of our environmental stress hypotheses because this variable could explain a large proportion of variance. 
Often the potential and the actual number of partners is the same or very close to each other, especially for rare species present only in a few communities.
As we were interested in understanding whether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we, therefore, included guild and its interaction with suitability in the model. 
We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate two questions. 
First, it allows us to inspect the extent to which suitability is a population or a group level effect. 
Second, by investigating the correlation between the intercept and the slope as a model parameter, it allowed us to inspect the extent by which species with a small or large number of interactions respond to increasing levels of environmental stress. 
To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we also calculated an intercept for each community in our study.
To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit standard deviation.
